\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-01 manuscript.Rmd

CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006] where 10 participants per parameters is required to earn trustworthiness of the result. Our sample size exceeds the requirement.

>>>>

CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006] where 10 participants per parameter is required to earn trustworthiness of the result. Our sample size exceeds the requirement.

### 2021-09-01 manuscript.tex

CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule (Bentler \& Chou, 1987; Jackson, 2003; Kline, 2015; Worthington \& Whittaker, 2006) where 10 participants per parameters is required to earn trustworthiness of the result. Our sample size exceeds the requirement.

>>>>

CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule (Bentler \& Chou, 1987; Jackson, 2003; Kline, 2015; Worthington \& Whittaker, 2006) where 10 participants per parameter is required to earn trustworthiness of the result. Our sample size exceeds the requirement.
